---
title: "Homework 5"
author: "Sihan Qiu"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

set.seed(1)
```

## Q1
```{r}
bdays_sim = function(n){

bdays = sample(1:365, size = n, replace = TRUE)

duplicate = length(unique(bdays)) < n  #check repeated birthdays
return(duplicate)
}

bdays_sim(10)
```

```{r, error=TRUE}
sim_res =
  expand_grid(
    n = c(2, 50),
    iter = 1:10000
  )|>
  mutate(res = map_dbl(n,bdays_sim))|>
  group_by(n)|>
  summarize(prob = mean(res))

sim_res|>
  ggplot(aes(x = n, y = prob))+
  geom_line()
```


## Q2

```{r}
t_sample = function(mu) {
  sample_data = rnorm(n = 30, mean = mu, sd = 5)
  t_result = broom::tidy(t.test(sample_data, mu = 0)) |>
  select(estimate, p.value)
  
  return(t_result)
}
```

```{r}
simulation_df = expand_grid(
  true_mu = 0:6,     
  iteration = 1:5000  
)
```

```{r}
simulation_results =
  simulation_df |>
  mutate(
    result = map(true_mu, t_sample)  
  ) |>
  unnest(result) 
```

```{r}
power_sum =
  simulation_results |>
  group_by(true_mu) |>
  summarize(
    power = mean(p.value < 0.05),  
    average_mu = mean(estimate),  
    .groups = "drop"
  )

```

## power of the test plot
```{r}
power_plot =
  ggplot(power_sum, aes(x = true_mu, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    x = "True Value of mu",
    y = "Power",
    title = "Power vs True mu"
  ) +
  theme_minimal()
power_plot
```

## average and true mean plot
```{r}
average_results = 
  simulation_results |>
  group_by(true_mu) |>
  summarize(
    average_mu = mean(estimate),  
    average_mu_rej = mean(estimate[p.value < 0.05], na.rm = TRUE),  
    .groups = "drop"
  )
```


```{r}
average_plot =
  ggplot(average_results) +
  geom_line(aes(x = true_mu, y = average_mu), color = "lightblue", linewidth = 1) +
  geom_point(aes(x = true_mu, y = average_mu), color = "lightblue") +
  geom_line(aes(x = true_mu, y = average_mu_rej), color = "red", linetype = "dashed", linewidth = 1) +
  geom_point(aes(x = true_mu, y = average_mu_rej), color = "red") +
  labs(
    title = "Average mu vs True mu",
    x = "True Value of mu",
    y = "Average mu"
  ) +
  theme_minimal()
average_plot
```
### Explainaiton
The sample average of mu across tests where the null is rejected is not equal to the true value of mu. Because the small sample size of mu, which makes the result bias (maybe distorted by some extreme values).





## Q3
```{r}
homicide = read.csv("homicide-data.csv")|>
  janitor::clean_names()
```

### description of the raw dataset
the raw dataset includes `r nrow(homicide)` observations, and `r ncol(homicide)` variables. Key variables includes homicides' id, dates, victims' names, race, age, sex, state, city, and disposition of homicides, and the specific location. 

```{r}
homicide_clean = 
  homicide |>
  mutate(
    victim_last = str_to_title((victim_last)),
    victim_first = str_to_title((victim_first)),
    city_state = paste(city, state, sep = ", ")
  )|>
  drop_na()
```


```{r}
homicide_clean|>
  group_by(city_state) |>
  summarise(
    total = n(),
    unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )
```

## proportion of baltimore
```{r}
baltimore_df = 
  homicide_clean|>
  filter(city_state == "Baltimore, MD")
```

```{r}
total_bal = nrow(baltimore_df)
unsolved_bal = sum(pull(baltimore_df, disposition) %in% c("Closed without arrest", "Open/No arrest"))
```

```{r}
prop_test = prop.test(x = unsolved_bal, n = total_bal)
prop_test_df = broom::tidy(prop_test)
```


## proportion of each city
```{r}
city_prop_test = 
  homicide|>
  mutate(
    victim_last = str_to_title(victim_last),
    victim_first = str_to_title(victim_first),
    city_state = paste(city, state, sep = ", ")  
  ) |>
  drop_na() |>
  
  group_by(city_state) |>
  summarise(
    total_homicide = n(),
    unsolved_homicide = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  ) |>
  mutate(
    prop_test = map2(unsolved_homicide, total_homicide, ~ prop.test(.x, .y)), 
    prop_test_tidy = map(prop_test, broom::tidy)  
  ) |>
  
  unnest(prop_test_tidy) |>
  
  select(city_state, total_homicide, unsolved_homicide, estimate, conf.low, conf.high) |>
  rename(
    estimated_proportion = estimate,
    conf_int_lower = conf.low,
    conf_int_upper = conf.high
  )

```


```{r}
city_prop_test =
  city_prop_test |>
  arrange(desc(estimated_proportion)) |>
  mutate(city_state = factor(city_state, levels = city_state)) 
```

## making a plot
```{r}
ggplot(city_prop_test, aes(x = city_state, y = estimated_proportion)) +
  geom_boxplot(aes(group = city_state), width = 0.6) +  
  geom_errorbar(aes(ymin = conf_int_lower, ymax = conf_int_upper), width = 0.3) +  
  labs(
    title = "Proportion of Unsolved Homicides by City",
    x = "City",
    y = "Estimated Proportion of Unsolved Homicides"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

